Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO: a Bayesian study

### 2016-04-13 Paper/paper.tex
alternative to multipanel fig.8
pdf plots for 80 events

\title{
Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO
}

@@

% {\it Left}:

@@

% {\it Right}: Filled-region plots showing the median and $90\%$ confidence intervals
% for $\lambdans$, as a function of the number of observed events $N$.
%  Shown are two independent filled regions. 
%  One in green shows the recovered confidence interval
%  for $\lambdans$ (on the left y-axis), normalized by its true value,
%  as a function of the 
%  number of observed events $N$. The recovered median is shown by the
%  green line-circled curve. The pair of horizontal green dashed (dotted)
%  lines show the $\pm 50\%$ ($\pm 25\%$) symmetric error bounds around
%  the true $\lambdans$ value, which is shown at y-value $=1$ by definition.
%  The second filled region, in grey, shows the recovered
%  confidence interval for neutron star compactness, without normalizing.
%  The corresponding y-values are shown on the *right* y-axis. The horizontal grey
%  dashed line traces the true value of $\lambdans$, and is what we expect
%  the filled region to approach with increasing number of observations.
%  Finally, the grey dotted lines are contours of $1/\sqrt{N}$, drawn to aid the eye.

@@

>>>>

\title{
Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO: a Bayesian study
}

@@

@@

@@

\includegraphics[width=1.05\columnwidth]{plots/FillBetweenRelErrorBarsLambda_vs_NShifted_AllLambda.pdf}
\label{fig:TT_Lambda_vs_N_CI90_0}
